|

### 2021-02-22 supplementary_information.Rmd
edits: SI, source file corrections

  # Hokkaido data
  dat_hkd <- read_csv(here::here('/empirical/data_out/dat_hkd_site.csv'))

  # Midwest data
  dat_mw <- read_csv(here::here('/empirical/data_out/dat_mw_site.csv'))

@@

  source(here::here('empirical/table_sim_parameter_sensitivity.R'))
  table_output

@@

  source(here::here('empirical/table_sim_parameter_main.R'))
  table_output

@@

source(here::here("/theory/figure_alpha_pattern.R"))

@@

source(here::here("/theory/figure_n_patch_si.R"))

@@

source(here::here("/theory/figure_p_branch_si.R"))

>>>>

  # Hokkaido data
  dat_hkd <- read_csv(here::here('empirical/data_out/data_hkd_site.csv'))

  # Midwest data
  dat_mw <- read_csv(here::here('empirical/data_out/data_mw_site.csv'))

@@

  source(here::here('theory/table_sim_parameter_sensitivity.R'))
  table_output

@@

  source(here::here('theory/table_sim_parameter_main.R'))
  table_output

@@

source(here::here("theory/figure_alpha_pattern.R"))

@@

source(here::here("theory/figure_n_patch_si.R"))

@@

source(here::here("theory/figure_p_branch_si.R"))
